---
title: "Automatic or Manual transmission better for MPG"
author: "SwhGo_oN"
date: "June 26, 2014"
output:
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
---

# Executive Summary

There is a set of variables related to miles per gallon (MPG) (outcome).

Here the difference of the MPG between automatic and manual transmissions is focused, 
the `mtcars` dataset in car package is taken as the data source, 
and techniques about regression models is used to solve the following two questions:

* “Is an automatic or manual transmission better for MPG”
*  “Quantifying how different is the MPG between automatic and manual transmissions?”


# Data Processing

## Load and Test Data

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r cache=TRUE}
library(datasets)
mpgData <- with(mtcars, data.frame(mpg, am))
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
#summary(mpgData)
```

## Process Data

### Q1: Is an automatic or manual transmission better for MPG?  

```{r cache=TRUE}
summary(mpgData[mpgData$am == "Automatic",])
summary(mpgData[mpgData$am == "Manual",])
```

### Q2: Quantifying how different is the MPG between automatic and manual transmissions?  

```{r cache=TRUE}
fit <- lm(mpg ~ as.integer(am), data=mpgData)
summary(fit)
```

# Results
So, manual transmission is better than automatic for MPG, which increased by `r coef(fit)[2]`.

# Appendix

## Fig 1. MPG between automatic and manual transmissions
```{r cache=TRUE}
par(mfrow=c(1,2))
with(mpgData,{
     boxplot(mpg ~ am, 
             ylab = "miles per gallon (MPG)")
     plot(mpg ~ as.integer(am),
             xlab = "Automatic (1) or Manual(2)",
             ylab = "miles per gallon (MPG)")
     abline(fit, col=2)
     })
```

## SourceCode
[part0_regmods-mtcars.Rmd](https://github.com/swhgoon/devdataprod-cp/blob/master/part0_regmods-mtcars/part0_regmods-mtcars.Rmd)

## Relationship between other variables and miles per gallon (MPG)
[part1_devdataprod-shiny](https://swhgoon.shinyapps.io/part1_devdataprod-shiny/)

